Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-24 journal-draft/ettdoc_JG.tex
modify section 4 and others

\begin{abstract}
%Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
%Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
%More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
%This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
%%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
%We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
%The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
%%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
%The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
%%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
%Extensive simulations are presented supporting the theoretical claims.
\end{abstract}

@@

We next focus on a single CR cluster. 
A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
The cluster head is able to communicate with any cluster member directly.
%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The number of nodes belonging to $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
The usage scope is also provided when they are not used throughout the paper.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
%$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the desired cluster size\\
$S_i$ & a set of claiming clusters, each of which \\
& includes debatable node $i$ after phase I\\
$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
& problem description (Sec.~\ref{problem})\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters \\
 & in $\mathcal{N}$ (Sec.~\ref{centralized_solution})\\
 $M$ & the cardinality of $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 %$|C_i|$ & the size of the cluster $C_i$\\
 %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 %$p(C_i)$ & the weight with respect to cluster $C_i$ (Sec.~\ref{centralized_solution}) \\
 $d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
  $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
 $J$ & the new value of $d_i$ for the CR node after it\\
 & becomes a cluster member (Sec.~\ref{ross})\\
% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
%XXXXXX%
%Di writes: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version. I take some parts from your revision and keep some from my revision.
We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
We initially consider a centralized solution for this problem.
Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
With $|\mathcal{S}| = M$, there is $\mathcal{S}=\{C_1, C_2, \ldots, C_M\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.}.
Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
\begin{equation}
%\begin{aligned}
%     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
%     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
%   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
%  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
%   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%%\notag
%\end{aligned}
\begin{aligned}
     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(C_i)) \\
     &\text{subject to}   && \Sigma_{i=1}^M (x_i\cdot e_{ij}) = 1  \quad\text{for}\,\,\forall j\in\{1, \ldots, N\} \\
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$x_i, i\in \{1,2, \cdots M\}$ is a set of binary optimization variables.
Being either 1 or 0, $x_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$e_{ij}, i\in \{1,2, \cdots M\}$ and $j=\{1, \ldots, N\}$ is a set of constants which indicate whether the CR node $j$ resides in the cluster $C_i$, \ie $e_{ij}=1$ means node $j$ resides in the cluster $C_i$, $e_{ij}=0$ indicates $j$ doesn't belong to that cluster .

@@

As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
For the second term in the bracket, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
There is, 
$$
p(C_i) = \rho(||C_i|-\delta|)
$$
where $\rho$ is a positive increasing function with respect to the the difference between $C_i$'s size and the desired size $\delta$.
When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
%The weight $p(C_i)$ with respect to different cluster sizes is as follows,

@@

\subsubsection{Determining Cluster Heads and Forming Clusters}
Given the connectivity vector per node, the procedure of determining cluster heads is as follows.
Each CR node decides whether it is a cluster head by comparing its connectivity vector with all neighboring connectivity vectors.
When CR node $i$ has lower individual connectivity degree than any of its neighbors except for those which have already been identified as cluster heads, node $i$ becomes a cluster head.
If there is a CR node $j$ in $i$'s neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ while the connectivity degree of $j$ is lower than for all other nodes in its neighborhood (except for nodes that already declared themselves as heads) then out of $i$ and $j$ the node with higher neighborhood connectivity degree will become cluster head.
If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
%
The node which is identified as cluster head broadcasts a message to notify its neighbors of this status update. 
As a consequence, all neighbors - which have not become cluster head themselves -  become cluster members of this cluster head.
In this step, nodes can become member of multiple clusters, depending on how many neighbors declare themselves as cluster heads.
\footnote{The issues arising out of cluster heads in the neighborhood of a newly formed cluster head are addressed in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning}}
During the whole phase I, whenever a CR node becomes cluster head, or the cluster composition changes, the cluster head broadcasts new/updated information about the cluster structure, in particular the new/updated sets of available channels regarding itself and all its cluster members.
Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is provided as Algorithm~\ref{alg0} in the appendix.

@@

In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, e)$ with the following elements:

\begin{itemize}
	\item $\mathcal{P}$, the set of players in the game, which are the debatable nodes in our problem.
	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, the set of the resources for players to choose. In our problem, $S_i$ is the set of the claiming clusters of $i$, and $\mathcal{R}$ is the set of all claiming clusters.
	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of the claiming clusters $S_i$.
	As debatable node $i$ is supposed to choose only one claiming cluster, only a single resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
	\item 	The cost function $e(C)$ regarding resource $C$. 
	$e(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
	As to cluster $C\in S_i$, the decrease of CCs caused by accepting the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
$i\rightarrow C$ means $i$ joins cluster $C$.
Obviously this function is non-decreasing with respect to the number of nodes joining cluster $C$.
\end{itemize}

@@

\subsection{Centralized Scheme vs. Decentralized Schemes}
We start with the comparison of the centralized scheme versus various distributed ones.
For this, we consider 10 primary users and 20 CR users are dropped randomly (with uniform distribution) in a square area where side length is $A$.
Transmission ranges of both primary and CR users are set to $A/3$.
By doing this, we abstract from the influence of any given physical layer technology and propagation environment parameters.
Due to the parameterization, on average 7 channels are available per CR node when the clustering process is started.
We set the desired cluster size $\delta$ as 3.
As for the centralized schemes, we set the following parameters numerically: $\rho_1 =  0.4$, $\rho_2 =  0.6$.

@@

Figure~\ref{size_control} provides further insights into the performance comparison.
Here, we depict the empirical cumulative distribution function of the size of the clusters.
%First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
The centralized schemes don't result in any singleton clusters in the the considered evaluation scenarios.
In contrast, ROSS-DGA/DFA account for 3\% singleton clusters of the total CR nodes, as compared to 10\% of nodes being unclustered when applying SOC.
ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in Section~\ref{ross_p1_guarantee_ccc} and Section~\ref{ross_p2_cluster_pruning}).
In terms of cluster size, the clusters resulting from the centralized schemes and ROSS with cluster size control mechanism have little deviation from the desired cluster size.
In contrast, the size of clusters resulting from ROSS-DGA and ROSS-DFA have a higher variance, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
Thus, the corresponding sizes resulting from ROSS are closer to the desired size.

@@

The empirical distribution functions (ECDF) associated with the cluster sizes show that the cluster sizes resulting from the variants of ROSS are clearly influenced by the chosen desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.
%Now we check how many CR nodes are in the clusters whose sizes deviate not much from the desired size, where we put the deviation limit at $\pm 50\%$ of the desired size.
The cluster sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrate more around the desired size than that of ROSS-DGA and ROSS-DFA.

>>>>

\begin{abstract}
Cluster structure in cognitive radio networks facilitates cooperative spectrum sensing, routing and other functionalities.
Unlicensed channels, which are temporally available for a group of cognitive radio users in one area, consolidate the group into a cluster.
More available unlicensed channels in a cluster make the cluster more likely to uphold against the licensed users' influence, making clusters more robust.
This paper analyses the problem of how to form robust clusters in a cognitive radio network such that cognitive radio systems benefit from collaboration within clusters despite intense primary user activity.
%In the process of forming clusters, every secondary user decides with whom to form a cluster, or which cluster to join.
We give a formal description of the robust clustering problem, prove it to be NP-hard and propose both centralized and distributed solutions.
The congestion game model is adopted to analyze the process of cluster formation, which not only contributes to the design of the distributed clustering scheme, but also provides a guarantee on the convergence to a Nash equilibrium and the convergence speed.
%Our proposed clustering solution is versatile to fulfill some other requirements such as faster convergence and cluster size control.
The proposed distributed clustering scheme outperforms state-of-the-art related works in terms of cluster robustness, convergence speed and overhead.
%Besides, we prove the clustering problem is NP-hard, and also propose the centralized solution.
Extensive simulations are presented supporting the theoretical claims.
\end{abstract}

@@

We next focus on a single CR cluster. 
A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
The cluster head is able to communicate with any cluster member directly.
%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The number of nodes belonging to $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
The usage scope is also provided when they are not used throughout the paper.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
%$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the desired cluster size\\
$S_i$ & a set of claiming clusters, each of which \\
& includes debatable node $i$ after phase I\\
$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
& problem description (Sec.~\ref{problem})\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters \\
 & in $\mathcal{N}$ (Sec.~\ref{centralized_solution})\\
 $M$ & the cardinality of $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 %$|C_i|$ & the size of the cluster $C_i$\\
 %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $p$ & the weight with respect to cluster's size (Sec.~\ref{centralized_solution}) \\
 $d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
  $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
 $J$ & the new value of $d_i$ for the CR node after it\\
 & becomes a cluster member (Sec.~\ref{ross})\\
% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
%XXXXXX%
%Di writes: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version. I take some parts from your revision and keep some from my revision.
We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
We initially consider a centralized solution for this problem.
Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
With $|\mathcal{S}| = M$, there is $\mathcal{S}=\{C_1, C_2, \ldots, C_M\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.}.
Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
\begin{equation}
%\begin{aligned}
%     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
%     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
%   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
%  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
%   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%%\notag
%\end{aligned}
\begin{aligned}
     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(||C_i|-\delta|)) \\
     &\text{subject to}   && \Sigma_{i=1}^M (x_i\cdot e_{ij}) = 1  \quad\text{for}\,\,\forall j\in\{1, \ldots, N\} \\
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$x_i, i\in \{1,2, \cdots M\}$ is a set of binary optimization variables.
Being either 1 or 0, $x_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$e_{ij}, i\in \{1,2, \cdots M\}$ and $j=\{1, \ldots, N\}$ is a set of constants which indicate whether the CR node $j$ resides in the cluster $C_i$, \ie $e_{ij}=1$ means node $j$ resides in the cluster $C_i$, $e_{ij}=0$ indicates $j$ doesn't belong to that cluster .

@@

As to the objective function, the sum of the first term in the bracket over all clusters in $\mathcal{S}$ is the sum of CCs of the clusters which constitute the CRN.
For the second term in the bracket, $p$ is a positive increasing function with respect to the the difference between $C_i$'s size and the desired size $\delta$.
When $x_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, the second item is negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from the desired cluster size $\delta$.
%The weight $p(C_i)$ with respect to different cluster sizes is as follows,

@@

\subsubsection{Determining Cluster Heads and Forming Clusters}
Given the connectivity vector per node, the procedure of determining cluster heads is as follows.
Each CR node decides whether it is a cluster head by comparing its connectivity vector with all neighboring connectivity vectors.
When CR node $i$ has lower individual connectivity degree than any of its neighbors except for those which have already been identified as cluster heads, node $i$ becomes a cluster head.
If there is a CR node $j$ in $i$'s neighborhood, which has the same individual connectivity degree as $i$, \ie $d_j = d_i$ while the connectivity degree of $j$ is lower than for all other nodes in its neighborhood (except for nodes that already declared themselves as heads) then out of $i$ and $j$ the node with higher neighborhood connectivity degree will become cluster head.
If $g_i = g_j$ as well, the node ID is used to break the tie, \ie the one with smaller node ID becomes the cluster head.
%
The node which is identified as cluster head broadcasts a message to notify its neighbors of this status update. 
As a consequence, all neighbors - which have not become cluster head themselves -  become cluster members of this cluster head.
In this step, nodes can become member of multiple clusters, depending on how many neighbors declare themselves as cluster heads.
\footnote{The issues arising out of cluster heads in the neighborhood of a newly formed cluster head are addressed in Section~\ref{ross_p1_guarantee_ccc} and \ref{ross_p2_cluster_pruning}}
During the whole phase I, whenever a CR node becomes cluster head, or the cluster composition changes, the cluster head broadcasts new/updated information about the cluster structure, in particular the new/updated sets of available channels regarding itself and all its cluster members.
Pseudo code regarding this process, i.e. the cluster head decision and the initial cluster formation, is in Algorithm~\ref{alg0} in appendix.

@@

In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, \rho)$ with the following elements:

\begin{itemize}
	\item $\mathcal{P}$, the set of players in the game, which are the debatable nodes in our problem.
	\item $\mathcal{R} = \cup S_i, i\in \mathcal{P}$, the set of the resources for players to choose. In our problem, $S_i$ is the set of the claiming clusters of $i$, and $\mathcal{R}$ is the set of all claiming clusters.
	\item Strategy space $\sum_i, i \in \mathcal{P}$, $\sum_i$ is the set of the claiming clusters $S_i$.
	As debatable node $i$ is supposed to choose only one claiming cluster, only a single resource will be allocated to $i$.%, accordingly this congestion game is a singleton game.
	\item 	The cost function $\rho(C)$ regarding resource $C$. 
	$\rho(C) = \Delta\vert K^i(C)|, C\in S_i$, which represents the decreased number of CCs in cluster $C$ when debatable node $i$ joins $C$.
	As to cluster $C\in S_i$, the decrease of CCs caused by accepting the debatable nodes is $\sum_{i:C\in S_i, i\rightarrow C} \Delta\vert K^i(C) \vert$. 
$i\rightarrow C$ means $i$ joins cluster $C$.
Obviously this function is non-decreasing with respect to the number of nodes joining cluster $C$.
\end{itemize}

@@

\subsection{Centralized Scheme vs. Decentralized Schemes}
We start with the comparison of the centralized scheme versus various distributed ones.
For this, we consider 10 primary users and 20 CR users are dropped randomly (with uniform distribution) in a square area where side length is $A$.
Transmission ranges of both primary and CR users are set to $A/3$.
By doing this, we abstract from the influence of any given physical layer technology and propagation environment parameters.
Due to the parameterization, on average 7 channels are available per CR node when the clustering process is started.
We set the desired cluster size $\delta$ as 3.
As for the centralized schemes, we set the following parameters numerically: $p(1) =  0.4$, $p(2) =  0.6$.

@@

Figure~\ref{size_control} provides further insights into the performance comparison.
Here, we depict the empirical cumulative distribution function (ECDF) of the size of the clusters.
%First, given the channel availability in the CRN, SOC generates more unclustered CR nodes than other schemes.
The centralized schemes don't result in any singleton clusters in the the considered evaluation scenarios.
In contrast, ROSS-DGA/DFA account for 3\% singleton clusters of the total CR nodes, as compared to 10\% of nodes being unclustered when applying SOC.
ROSS-DGA and ROSS-DFA with size control feature generate 5\%-8\% unclustered CR nodes, which is due to the cluster pruning procedure (discussed in Section~\ref{ross_p1_guarantee_ccc} and Section~\ref{ross_p2_cluster_pruning}).
In terms of cluster size, the clusters resulting from the centralized schemes and ROSS with cluster size control mechanism have little deviation from the desired cluster size.
In contrast, the size of clusters resulting from ROSS-DGA and ROSS-DFA have a higher variance, but appear to be better than SOC, i.e., the 50\% percentiles for ROSS-DGA, ROSS-DFA and SOC are 4.5, 5, and 5.5, and the 90\% percentiles for the three schemes are 8, 8, and 9.
Thus, the corresponding sizes resulting from ROSS are closer to the desired size.

@@

The ECDF associated with the cluster sizes show that the cluster sizes resulting from the variants of ROSS are clearly influenced by the chosen desired size, \ie as shown in Figures~\ref{cdf_clusterSize_100}, where the number of CR nodes is 100 and the desired cluster size is 6, 90\% of CR nodes are in clusters whose sizes are between 3 and 9, while for SOC, only 17\% of nodes are in the clusters with these sizes.
Similarly, when $N=200$ and the desired size is 12 (as shown in Figure~\ref{cdf_clusterSize_200}), 80\% of nodes are in clusters whose sizes are between 6 and 18, while only 30\% of nodes are in clusters of similar sizes when SOC is executed.
%Now we check how many CR nodes are in the clusters whose sizes deviate not much from the desired size, where we put the deviation limit at $\pm 50\%$ of the desired size.
The cluster sizes from ROSS-$\delta$-DGA and ROSS-$\delta$-DFA concentrate more around the desired size than that of ROSS-DGA and ROSS-DFA.
